The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-11 src/rev1_reply_comments.tex
Update references.
Add summary.

\large{\textbf{\textcolor{red}{SUMMARY}}}

@@

              We base our assumption on infectiousness being independent of age on
              \citet{Jones2021}. That study was the only one we could find that was able
              to differentiate between age differences in susceptibility (given a risk
              contact) vs. age differences in contact patterns. Moreover, they had fine
              grained age bins. That paper reports only slight differences in viral
              loads between German adults and children: ``The least infectious youngest
              children have 78\% (61, 94) of the peak culture probability of adults aged
              45 to 55''. Furthermore, they caution that these lower numbers may be due
              to different sample taking---such as the usage of smaller pediatric swab
              devices---rather than actual lower viral loads and conclude that the
              differences, if existent, are likely not clinically relevant. In fact,
              \citet{Goldstein2021}  reach similar conclusions, writing: \textit{``There
                  is limited evidence in the literature regarding age-related differences in
                  infectivity, although point estimates in several studies suggest that
                  infectivity may increase somewhat with age.''} We are thus confident that
              different assumptions in the range of plausible values would not
              change our results in a quantitatively meaningful way.

>>>>

\section*{Summary}

We thank the editors and referees for their excellent comments. Revising the
paper to address them has allowed us to substantially improve our paper.

% strongest change came through sensitivity comment
The largest adjustment was warrented with respect to the sensitivity of rapid
tests. We fully agree that our calibration appears optimistic in light of the
studies that have come out since our submission. We therefore verified that 
our results and conclusions are not affected when repeating the simulations 
with rapid tests with a much lower sensitivity. For that, we added a robustness
check with sensitivities that are derived from more recent
sources, relying on the progression of viral load over the course of an
infection and rapid test sensitivity with respect to different viral loads. 
These new sensitivities are on average significantly lower than those in our 
main specification. We are happy to report that even the most conservative 
estimates only lead to a small decrease in the estimated role of rapid tests.

The remaining comments have allowed us to improve our text significantly to be
clearer and better referenced. We also updated our citations for papers that we
had cited as pre-prints and that have been published in the meantime.
In our view the text has become clearer, more legible and better referenced 
as a result.

@@

              We base our assumption on infectiousness being independent of age on
              \citet{Jones2021}. That paper reports only slight differences in viral
              loads between German adults and children: ``The least infectious youngest
              children have 78\% (61, 94) of the peak culture probability of adults aged
              45 to 55''. Furthermore, they caution that these lower numbers may be due
              to different sample taking---such as the usage of smaller pediatric swab
              devices---rather than actual lower viral loads and conclude that the
              differences, if existent, are likely not clinically relevant.

              In fact,
              \citet{Goldstein2021}  reach similar conclusions, writing: \textit{``There
                  is limited evidence in the literature regarding age-related differences in
                  infectivity, although point estimates in several studies suggest that
                  infectivity may increase somewhat with age.''} We are thus confident that
              different assumptions in the range of plausible values would not
              change our results in a quantitatively meaningful way.
